---
title: "Instructions for Using the `powers` package"
author: "Mar Bazua-Lobato"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package was developed as an assignment. It's not a serious package.

With this package you can: square, cube, and compute the reciprocal of a vector. You can also apply a Box-Cox transformation to a vector and find the solution of a second degree polynomial. 

By just using a function!

```{r}
library(powers)
```

To compute squares, cubes, or reciprocals: 

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

Want to plot the results?
```{r}
square(1:10, add_plot=TRUE)
cube(1:10, add_plot=TRUE)
reciprocal(1:10, add_plot=TRUE)
```

For applying a Box-Cox transformation just use the `box_cox()` function :
```{r}
box_cox(1:10, 3)
```

Want to plot the transformed vector?
```{r}
box_cox(1:10, 3, add_plot=TRUE)
```

Do you want to obtain the roots of $8x^2+9x+1=0$?
Just use `polynom()`:
```{r}
polynom(8,9,1)
```


